Scalable and Parameter-Free Exploration in Deep Reinforcement Learning

### 2022-01-11 papers/main.tex
TEMPORARY DEPLOY COMMIT

\subsection{Functional Variational Bayesian Neural Networks}
There are several ways of approximating the posterior distribution of the weights
in a neural network with respect to a prior and a dataset. Typically, the dataset
\(\D\) is static and with datapoints \(\bm{x}\) and labels \(\bm{y}\), and the 
prior is defined as a distribution over the weights
\(p(\bm{w})\)~\citep{rezende_stochastic_2014,blundell_weight_2015,ritter_scalable_2018,maddox_simple_2019}.

Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
a variational inference method for neural networks that approximates the 
posterior distribution in function space.
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):

\begin{equation}
    \KL[P \Vert Q] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ P_\X \Vert Q_\X \right],
\end{equation}

>>>>

\subsection{Functional Variational Bayesian Neural Networks}
There are several ways of approximating the posterior distribution of the weights
in a neural network with respect to a prior and a dataset. Typically, the dataset
\(\D\) is static and with datapoints \(\bm{x}\) and labels \(\bm{y}\), and the 
prior is defined as a distribution over the weights
\(p(\bm{w})\)~\citep{rezende_stochastic_2014,blundell_weight_2015,ritter_scalable_2018,maddox_simple_2019}.
By defining a prior over the weights, they can use approximate variational inference
methods to approximate \(p(\bm{w} \vert \D) = \frac{p(\D \vert \bm{w})p(\bm{w})}{p(\D)}\).
The disadvantage of this is that \(p(\bm{w})\) only acts as a regularizer, and is not
used to incorporate prior knowledge. Any prior knowledge we might have about the optimizer
function would be very difficult to translate into a prior distribution in the weight space.

Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
a variational inference method for neural networks that approximates the 
posterior distribution in function space. This means that our prior will be a distribution
over functions, also known as a stochastic process.
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):

\begin{equation}
    \KL[Q \Vert P] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ Q_\X \Vert P_\X \right],
\end{equation}
